Depression and suicidality as credible signals of need

### 2021-05-06 Paper.rmd
Added limitation and notes

Another limitation is that our control included a signal in the form of a verbal request, preventing comparisons to non-signaling strategies. Similarly, our design did not include vignettes with male signalers. For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.

@@

# Conclusion

>>>>

Another limitation is that our control included a signal in the form of a verbal request, preventing comparisons to non-signaling strategies. Similarly, our design did not include vignettes with male signalers. For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined. Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex suffered greater negative reputational effects due to emotions and behaviors in the vignettes. It is also possible the costliness of the situations presented in the vignettes differ by sex.

@@

Slider anchor 
Regex: stopped in SI
T\d \w+
# Conclusion
